Self Regulation Ontology Retest Data Report

### 2018-02-19 code/SRO_Report.Rmd
updating report w new data

>>>>

```{r}
boot_df
```

## Survey reliabilities

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'survey') %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            min_icc = min(icc),
            max_icc = max(icc),
            min_spearman = min(spearman),
            max_spearman = max(spearman),
            num_measures = n()/1000)%>%
  arrange(-median_icc, -median_spearman)

sjt.df(tmp %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/survey_rel_table.doc")
```
